\MakeUppercase{Measuring polygonal niceness} \thanks{ This paper comprises the completion of the final project for AMS 545 ``Computational Geometry''. }

### 2018-05-04 paper/main.tex
Changed some stuff
Updates to the paper.
Section 3 is done, section 4 is almost done. I am just generating some final plots and putting them into the paper. Then the only things that remain are the introduction and conclusion sections.

\documentclass[draft]{jocg}

@@

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage[mathlines]{lineno}
\linenumbers

@@

\begin{abstract}
  In which I do all of the work and my partner free loads on literally every
  piece of this project.
\end{abstract}

@@

\begin{enumerate}
  \item Paragraph explaining discretization procedure.
  \item Pseudocode and explanation for the alpha fatness.
  \item Pseudocode and explanation for the chord $f$ score.
  \item Formulate ``random'' polygons.
  \item Explain U.S. state boundary data collection.
\end{enumerate}

@@

@@

\begin{enumerate}
  \item Comment on the results.\cite{cgal:eb-18a}
  \item Talk about applications to Gerrymandering.\cite{cgal:gw-p2-18a}
\end{enumerate}

>>>>

\documentclass[]{jocg}

@@

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage[mathlines]{lineno}
\usepackage[]{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\linenumbers

@@

\begin{abstract}
\end{abstract}

@@

In principal of computing the $\alpha$ and chord-$f$ scores relies on sweeping
the continuum of points of $P$ and evaluating the aforementioned measurements.
To estimate this process in practice, we employ the following discretizing
scheme. Let $P$ be determined by the vertices $[v_1, \dots, v_n]$ given in
counterclockwise order. Then, given $\delta > 0$, loop through the vertices of
$P$, checking if $\norm{v_{i+1} - v_i} > \delta$. In the case where this holds,
we insert $v_i' = \frac{v_i + v_{i+1}}{2}$ after $v_i$ into the polygon and
resume the loop. This ensures that for any two adjacent vertices $v_{i}$ and
$v_{i+1}$ in the representation of $P$ we have $\norm{v_{i+1} - v_i} \leq
\delta$. As $\delta \to 0$ this estimates $\partial P$ more exactly. All
computations are done with respect to the $L_{\infty}$ norm. The implementation
of this procedure is given in Algorithm \ref{alg:delta}.

%% Pseudocode for the delta refinement

\begin{algorithm}[h]
  \begin{algorithmic}[0]
    \Procedure{RefineBy}{$P,\delta$}
    \State{$P = [v_1, v_2, v_3, \dots, v_n]$};
    \State{$v = v_1$}
    \While {$\textit{next}(v) \ne v_1$}
    \If {$\norm{\textit{next}(v) - v}_2 > \delta$}
      \State{\textrm{Insert $\textit{midpoint}(v, \textit{next}(v))$ into $P$
      after $v$}} 
      \Comment{Now $\textit{next}(v)$ is the midpoint}
      \EndIf
      \EndWhile
      \EndProcedure
    \end{algorithmic}
    \label{alg:delta}
\end{algorithm}

Given a $\delta$-refined polygon $P$, the computation of $\alpha(P)$ is
relatively straightforward, with the simplification that points $x$ on which the
ratio is computed lie on $\partial P$. The computation steps through $[v_1,
\dots, v_n]$ and for each $v_i$ the radius $\varepsilon$ of the
minimum-enclosing $\infty$-ball centered at $v_i$ is computed. Then for
$\varepsilon_k = \frac{k}{100} \varepsilon$, $k = 1, \dots, 100$, the ratio 
\begin{equation*}
  \frac{\lambda[P \cap B_{\infty}(v_i, \varepsilon_k)]}{B_{\infty}(v_i,
  \varepsilon_k)}
\end{equation*}
is computed and the smallest such ratio is kept. The minimum over all $v_i$ is
given as $\alpha(P)$. The implementation of the $\alpha$ score is given in
Algorithm \ref{alg:alpha}.

%% Pseudocode for the alpha score

\begin{algorithm}[h]
  \begin{algorithmic}[0]
    \Function{$\alpha$Score}{$P$}
    \State{$P = [v_1, v_2, v_3, \dots, v_n]$};
    \State{$\textrm{min} = \infty$}
    \For {$v \in P$}
    \State{$\varepsilon = \textrm{radius of minimum enclosing ball of $P$ at
    $v$}$}
    \For {$k = 1, 2, \dots, 100$} \Comment{$100$ is arbitrary}
    \State{$\varepsilon_k = \frac{k}{100} \varepsilon$}
    \State{$\textrm{area} = \frac{\lambda[P \cap B_{\infty}(v, \varepsilon_k)]}{B_{\infty}(v, \varepsilon_k)}$}
    \If {$\textrm{min} > \textrm{area}$}
      \State{$\textrm{min} = \textrm{area}$}
      \EndIf
      \EndFor
      \EndFor
      \State{\Return{\textrm{min}}}
      \EndFunction
    \end{algorithmic}
  \label{alg:alpha}
\end{algorithm}

Similarly, given a $\delta$-refined polygon $P$, the chord-$f$ score is computed
by sweeping all possible chords of $P$. For each point $v_i, v_j \in \partial P$
with $i < j$, if $[v_i, v_j]$ is indeed a valid chord of $P$, the partition $P =
P' \cup P''$ is computed and the maximum of $f(P')$ and $f(P'')$ is kept. The
minimum such value is given as $s_f(P)$. The implementation of the chord-$f$
score is given in Algorithm \ref{alg:chordf}.

%% Pseudocode for the chord f score

\begin{algorithm}[h]
\begin{algorithmic}[0]
  \Function{ChordScore}{P,f}
  \State{$P = [v_1, v_2, v_3, \dots, v_n]$};
  \For {$v \in P$}
  \For {$w \in [\textit{next}(v), \dots, v_n]$}
  \If {$[v,w]$ is a chord of $P$}
    \State{Partition $P = P' \cup P''$ by $[v,w]$}
    \State{$\textrm{submax} = \textit{max}(f(P'), f(P''))$}
    \If {$\textrm{min} > \textrm{submax}$}
      \State{$\textrm{min} = \textrm{submax}$}
      \EndIf
    \EndIf
  \EndFor
  \EndFor
  \State{\Return{\textrm{min}}}
  \EndFunction
\end{algorithmic}
\label{alg:chordf}
\end{algorithm}

All of these algorithms are implemented in CGAL \cite{cgal:eb-18a} with the
extensive use of the 2D Polygon library \cite{cgal:gw-p2-18a}.

@@

We evaluate our measurements on randomly generated polygons with vertices in the
unit square $[0,1] \times [0,1]$. We consider collections of such polygons of
10, 50, and 100 vertices. In Figure \ref{fig:delta}, we measure the effect of
sweeping $\delta$ between $0.05$ and $1$ on the resulting measurements. Figure
\ref{fig:alph-inft-10} shows a comparison of $\alpha$-fatness and
${\chordarc}_{\infty}$ scores for polygons on 10 vertices. Figure
\ref{fig:alph-one-50} shows a similar comparison of $\alpha$-fatness and
${\chordarc}_{1}$ scores for polygons on 50 vertices.

\begin{figure}[t]
  \centering
  %\includegraphics{<+file+>}
  \caption{Effect of sweeping $\delta$ on measurements}
  \label{fig:delta}
\end{figure}<++>

\begin{figure}[t]
  \centering
  \includegraphics[height=0.8\textheight]{../plots/u_10_alpha_score_chord_arc_infinity_vertices_0-05_delta_ranking.jpg}
  \caption{$\alpha$ scores and ${\chordarc}_{\infty}$ scores for randomly
  generated polygons on 10 vertices.}
  \label{fig:alph-inft-10}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[height=0.8\textheight]{../plots/u_50_alpha_score_chord_arc_one_vertices_0-05_delta_ranking.jpg}
  \caption{$\alpha$ scores and ${\chordarc}_{\infty}$ scores for randomly
  generated polygons on 50 vertices.}
  \label{fig:alph-inft-10}
\end{figure}

@@

\begin{enumerate}
  \item Comment on the results.
  \item Talk about applications to Gerrymandering.
\end{enumerate}
